MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex
adding makefile, citations, and cleanups

To test the system, we use a variety of different sets of images.
These images were obtained from
Flickr\footnote{\url{http://www.flickr.com/}} and \code{memebase.com},
using a public API and a Python script \cite{flickerpy} to get test
data.  We converted animated GIFs into individual frames again using a
preprocessing phase.  Our MapReduce code takes as input simply a
\code{SequenceFile} (as discussed in Section~\ref{sec:conversion}), so
we simply feed in a folder of JPG images to our preprocessing phase.

>>>>

To test the system, we use a variety of different sets of images.
These images were obtained from
Flickr\footnote{\url{http://www.flickr.com/}} and \code{memebase.com},
using a public API and a Python script \cite{flickrpy} to get test
data.  We converted animated GIFs into individual frames again using a
preprocessing phase.  Our MapReduce code takes as input simply a
\code{SequenceFile} (as discussed in Section~\ref{sec:conversion}), so
we simply feed in a folder of JPG images to our preprocessing phase.
